PK object batch mode trial

### 2023-07-19 data-raw/batchMode_trial_gpm.Rmd
Updating do_process to account for group-based Time Unit conversions and re-fitting cvt data

my_predata <- cvt %>%
  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% c("DTXSID0020442",
                                                              "DTXSID5032600",
                                                              "DTXSID2021103"))
my_predata <- cvt %>%
  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID1043881")

@@

```{r single_fit}
my_pk <- pk(data = my_predata) +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = TRUE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
  scale_time(new_units = "days") +
  # stat_model() + 
  stat_error_model(error_group = vars(Chemical, Species)) 
# Add Reference for Joint Analysis

@@

my_IC %>% group_by(Chemical, Species, method) %>%
  filter(AIC == min(AIC),
         method == "bobyqa") %>%
  ungroup() %>%
  count(model)
# model_1comp 60
# model_2comp 48
# model_flat   3

my_IC %>% group_by(Chemical, Species, method) %>%
  filter(AIC == min(AIC),
         method == "L-BFGS-B") %>%
  ungroup() %>%
  filter(model == "model_flat") %>% pull(Chemical) %>% unique()
  count(model)
# model_1comp 56
# model_2comp 50
# model_flat   5

@@

@@

my_preds <- inner_join(winmodels, my_preds)
my_tkstats <- inner_join(winmodels, my_tkstats) %>%
  dplyr::select(-TKstats, -Reference) %>% distinct()
my_nca <- get_nca(my_pk,
                  nca_group = vars(Chemical, Species,))
my_nca <- my_nca %>% dplyr::select(-param_sd_z, -param_units) %>%
  pivot_wider(names_from = param_name,
              values_from = param_value)

@@

my_preds %>%
  rowwise() %>%
  mutate(Pred_Obs = Conc_trans/Conc_est) %>%
  filter(is.finite(Pred_Obs),
         model %in% c("model_1comp", "model_2comp")) %>%
  # mutate(pass = ifelse(Pred_Obs <= 2 & Pred_Obs >= 0.5, TRUE, FALSE)) %>%
  # pull(pass) %>% table()
  ggplot(aes(x = Pred_Obs)) +
  geom_histogram(binwidth = 0.4,
                 fill = "grey5") +
  scale_x_log10(limits = c(NA, 1E6)) +
  expand_limits(y = 0) +
  geom_vline(xintercept = c(0.5, 2), color = "red3", linetype = "dashed") +
  facet_grid(cols = vars(model),
             rows = vars(Route)) +
  labs(x = "Predicted/Observed",
       y = "Number of Observations") +
  theme_classic() +
  theme(aspect.ratio = 1,
        panel.border = element_rect(color = "black", fill = NA),
        panel.grid.major = element_line(color = "grey90", linewidth = 0.4))

# 89.9% of Pred_Obs are finite
# 19.3% Are below two-fold
# 34.8%  Are above two-fold
# 45.9% Are within twofold

ggsave(paste0("C:/Users/GPADILLA/OneDrive - Environmental Protection Agency (EPA)/Profile/Documents/Figures/",
              "PredictedObserved_compartmentModels_2023-07-11.png"),
       height = 4, width = 9)

@@

```{r update_eval_kstats}
devtools::load_all()
my_eval <- eval_tkstats(my_pk)

@@

ggplot(my_eval,
       aes(x = AUC_inf_RMSE,
           y = Cmax_RMSE)) +
  geom_point()

@@

```{r eval_Joint}
my_pk <- readRDS("data-raw/all_cvt_pk_JOINT.rds")
my_eval_joint <- eval_tkstats(my_pk)

@@

total_eval %>%
  dplyr::select(!Cmax_RMSE) %>%
  pivot_wider(names_from = Analysis_Type,
              values_from = AUC_inf_RMSE) %>%
  ggplot(aes(x = -log10(Pooled),
             y = -log10(Joint),
             color = Media)) +
  geom_point(alpha = 0.3) +
  geom_abline(slope = 1, linetype = "dashed") +
  facet_grid(rows = vars(model),
             cols = vars(method)) +
  theme(panel.border = element_rect(color = "black", fill = NA, size = 1.5),
        panel.background = element_blank(),
        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
        strip.background = element_rect(fill = "white"),
        axis.ticks = element_blank(),
        axis.line = element_blank())

total_eval %>%
  dplyr::select(!Cmax_RMSE) %>%
  pivot_wider(names_from = Analysis_Type,
              values_from = AUC_inf_RMSE) %>%
  mutate(ratio = Joint/Pooled) %>%
  filter(!(ratio == 1)) %>% pull(Chemical) %>% unique()
  View()

>>>>

my_predata <- cvt %>%
  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% c("DTXSID0020442",
                                                              "DTXSID5032600",
                                                              "DTXSID2021103"))
my_predata <- cvt %>%
  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID9021924")

@@

```{r single_fit}
# Pooled
my_pk <- pk(data = my_predata) +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = TRUE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
  # scale_time(new_units = "auto") +
  # stat_model() + 
  stat_error_model(error_group = vars(Chemical, Species)) 
# Add Reference for Joint Analysis

my_pk <- do_fit(my_pk)

# Joint
my_pk <- pk(data = cvt) +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = TRUE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
  # scale_time(new_units = "auto") +
  # stat_model() + 
  stat_error_model(error_group = vars(Chemical, Species, Reference)) 
# Add Reference for Joint Analysis

@@

my_IC %>% group_by(Chemical, Species, method) %>%
  filter(AIC == min(AIC),
         method == "bobyqa") %>%
  ungroup() %>%
  count(model)
# model_1comp 59
# model_2comp 50
# model_flat   2

my_IC %>% group_by(Chemical, Species, method) %>%
  filter(AIC == min(AIC),
         method == "L-BFGS-B") %>%
  ungroup() %>%
  # filter(model == "model_flat") %>% pull(Chemical) %>% unique()
  count(model)
# model_1comp 57
# model_2comp 50
# model_flat   4

@@

all_my_data %>%
  group_by(Chemical,
           Species,
           Reference,
           Route,
           Dose, Time) %>%
  filter(n() > 1,
         sum(is.na(Conc)) != n(),
         exclude == FALSE) %>%
  mutate(meanConc = mean(Conc, na.rm = TRUE)) %>%
  ungroup() %>%
  rowwise() %>%
  mutate(foldConc = Conc / meanConc) %>%
  inner_join(my_tkstats %>%
              dplyr::select(Chemical, Species,
                            Route, Media,
                            tmax) %>%
              filter(!is.na(tmax))) %>%
  group_by(Chemical,
           Species,
           Reference,
           Route,
           Media,
           Dose) %>%
  mutate(
         normTime = ifelse(
           Route == "iv",
           1 + Time/max(Time),
           ifelse(
             Time > tmax,
             ((Time - tmax)/max(Time)) + 1,
             0.5 + Time/(2*tmax)
           )
         )) %>%
  ggplot(aes(
    x = normTime,
    y = foldConc
  )) +
  geom_point(alpha = 0.2) +
  geom_vline(xintercept = 1, color = "blue", linetype = "dashed") +
  geom_vline(xintercept = 2, color = "green4", linetype = "dashed") +
  geom_hline(yintercept = c(0.5, 2), color = "red3", linetype = "dashed") +
  facet_grid(cols = vars(Route),
             scales = "free_x") +
  labs(x = "ADME-Normalized Time",
       y = "Mean-Normalized Concentration") +
  theme(aspect.ratio = 1,
        panel.border = element_rect(color = "black", fill = NA, size = 1.5),
        panel.background = element_blank(),
        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
        strip.background = element_rect(fill = "white"),
        strip.text = element_text(face = "bold"),
        axis.ticks = element_blank(),
        axis.line = element_blank(),
        axis.text.x = element_blank())

ggsave(paste0("C:/Users/GPADILLA/",
              "OneDrive - Environmental Protection Agency (EPA)/",
              "Profile/Documents/Figures/",
              "ADME_NormalizedTime-NormalizedConcentrations_2023-07-19.png"),
       height = 4,
       width = 6,
       units = "in")

my_tkstats %>%
              dplyr::select(Chemical, Species,
                            Route, Media, model, method,
                            tmax) %>%
              filter(!is.na(tmax))

all_my_data %>%
              dplyr::select(Chemical, Species,
                            Route, Media, Dose,
                            Reference) %>%
  distinct() %>% nrow()

@@

my_preds <- inner_join(winmodels, my_preds)
my_tkstats <- inner_join(winmodels, my_tkstats) %>%
  dplyr::select(-TKstats) %>% distinct()
my_nca <- get_nca(my_pk,
                  nca_group = vars(Chemical, Species,))
my_nca <- my_nca %>% dplyr::select(-param_sd_z, -param_units) %>%
  pivot_wider(names_from = param_name,
              values_from = param_value)

@@

my_preds %>%
  rowwise() %>%
  mutate(Pred_Obs = Conc_trans/Conc_est) %>%
  filter(is.finite(Pred_Obs),
         model %in% c("model_1comp", "model_2comp")) %>%
  # mutate(pass = ifelse(Pred_Obs < 0.5, TRUE, FALSE)) %>%
  # pull(pass) %>% table()
  ggplot(aes(x = Pred_Obs)) +
  geom_histogram(binwidth = 0.4,
                 fill = "grey5") +
  scale_x_log10(limits = c(NA, 1E6)) +
  expand_limits(y = 0) +
  geom_vline(xintercept = c(0.5, 2), color = "red3", linetype = "dashed") +
  facet_grid(cols = vars(model),
             rows = vars(Route)) +
  labs(x = "Predicted/Observed",
       y = "Number of Observations") +
  theme_classic() +
  theme(aspect.ratio = 1,
        panel.border = element_rect(color = "black", fill = NA),
        panel.grid.major = element_line(color = "grey90", linewidth = 0.4))

# 91.1% of Pred_Obs are finite
# 16.6% Are below two-fold
# 33.2%  Are above two-fold
# 50.2% Are within twofold

ggsave(paste0("C:/Users/GPADILLA/",
              "OneDrive - Environmental Protection Agency (EPA)/",
              "Profile/Documents/Figures/",
              "PredictedObserved_compartmentModels_2023-07-11.png"),
       height = 6, width = 7)

@@

```{r update_eval_tkstats}
devtools::load_all()
my_pk <- readRDS("data-raw/all_cvt_pk.rds")
my_eval <- eval_tkstats(my_pk)

@@

ggplot(my_eval,
       aes(x = AUC_inf_RMSE,
           y = Cmax_RMSE)) +
  geom_point() +
  geom_abline(slope = 1) +
  scale_y_log10() +
  scale_x_log10()

@@

```{r eval_Joint}
my_pk2 <- readRDS("data-raw/all_cvt_pk_JOINT.rds")
my_eval_joint <- eval_tkstats(my_pk2)

@@

total_eval %>%
  dplyr::select(!Cmax_RMSE) %>%
  pivot_wider(names_from = Analysis_Type,
              values_from = AUC_inf_RMSE) %>%
  ggplot(aes(x = log10(Pooled),
             y = log10(Joint),
             color = Media)) +
  geom_point(alpha = 0.3) +
  geom_abline(slope = 1, linetype = "dashed") +
  facet_grid(rows = vars(model),
             cols = vars(method)) +
  theme(panel.border = element_rect(color = "black", fill = NA, size = 1.5),
        panel.background = element_blank(),
        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
        strip.background = element_rect(fill = "white"),
        axis.ticks = element_blank(),
        axis.line = element_blank())

total_eval %>%
  dplyr::select(!Cmax_RMSE) %>%
  pivot_wider(names_from = Analysis_Type,
              values_from = AUC_inf_RMSE) %>%
  mutate(ratio = Joint/Pooled) %>%
  # filter(!(ratio == 1)) %>% 
  # View()
  pull(Chemical) %>%
  # unique()
  length()
